Random Forests", OAs

### 2025-01-21 presentations/old/web_diffusion.Rmd
early/late

---
title: 'A multi-scale story of the diffusion of a new technology: the web'
# date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
author: |
  |
  | Emmanouil Tranos
  |
  | <small>University of Bristol, Alan Turing Institute</small>
  | <small>e.tranos@bristol.ac.uk, [\@EmmanouilTranos](https://twitter.com/EmmanouilTranos), [etranos.info](https://etranos.info/)</small>
output: 
  revealjs::revealjs_presentation:
    theme: simple
    self_contained: true
    reveal_options:
      width: 1150
      height: 720
bibliography: bibliography.bib
biblio-style: "apalike"
css: style.css
editor_options: 
  markdown: 
    wrap: 72
---

@@

::: {style="margin-left: 50px !important; text-align:left !important"}
-   Introduction

-   Web data

-   Methods

-   Results

    -   S-shaped diffusion curves
    -   Rank dynamics
    -   Exploratory spatial analysis
    -   Modelling

-   Conclusions <br> <br>
    <!-- [etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/) -->
:::

@@

## Aim

@@

@@

## Diffusion of a new *digital* technology

-   Diffusion of an **intangible**, digital technology [*web*]

-   Map the **active** engagement with the *digital*

-   Over time, **early stages** of the internet [*1996-2012*]

-   Granular and multi-scale **spatial processes**

@@

-   Data from the Internet Archive, the oldest web archive

@@

-   Geolocation: postcode references in the text

-   Timestamp: archival year

-   Counts

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
![](images/Picture1.png){width="70%"}

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
![](images/Picture2.png){width="70%"}

-   Data from a Web Archive -- The Internet Archive

-   Geolocation: postcode references in the text

-   Timestamp: archival year

-   Counts

@@

@@

<!-- <small> -->

<!-- -   Tranos, E., and C. Stich. 2020. Individual internet usage and the -->

<!--     availability of online content of local interest: A multilevel -->

<!--     approach. *Computers, Environment and Urban Systems*, 79:101371. -->

<!-- -   Tranos, E., T. Kitsos, and R. Ortega-Argilés. 2021. Digital economy -->

<!--     in the UK: Regional productivity effects of early adoption. -->

<!--     *Regional Studies*, 55:12, 1924-1938. -->

<!-- -   Stich, C., E. Tranos and M. Nathan. 2022. Modelling clusters from -->

<!--     the ground up: a web data approach. *Environment and Planning B*, in -->

<!--     press. -->

<!-- -   Tranos, E., A. C. Incera and G. Willis. 2022. Using the web to -->

<!--     predict regional trade flows: data extraction, modelling, and -->

<!--     validation, *Annals of the AAG*, in press. -->

<!-- </small> -->

@@

20080509162138 \| <http://www.website1.co.uk/contact_us> \| IG8 8HD

@@

# load 2000 co.uk
# path.2000 <- "C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/all2000couk.csv"
# path.2000 <- "/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/all2000couk.csv"
path.2000 <- paste0(path, "/data/temp/all2000couk.csv")

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->
![](images/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->
![](images/screenshot_2010.png)

# Methods

## Reminder: diffusion mechanisms

-   **S-shaped** pattern in the cumulative level of adoption

-   A **hierarchy effect**: from main centres to secondary ones

-   A **neighborhood effect**: first "hitting" nearby locations

## Methods

-   Cumulative adoption: Self-starting logistic growth model [`nls` and
    `SSlogis`]

-   Descriptive statistics & ESDA

-   Machine learning framework [random forests]

-   Two scales:

    -   websites per firm in a Local Authority
    -   websites in an Output Area

@@

```{r UK S, eval=T, out.width = "60%", out.height="60%"}
#, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"

path.image <- paste0(path, "/outputs/s_uk_per_firm.png")
knitr::include_graphics(path.image)
```

```{r LA_S_gif, eval=F, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/s_lad_per_firm/")

library(magick)
las <- list.files(path = path.images, pattern = "^lad_", full.names = T) 
las <- sample(las, 50)
las_list <- lapply(las, image_read)

@@

## animate at 2 frames per second
las_animated <- image_animate(las_joined, fps = 4)

## view animated image
#las_animated

## save to disk
# image_write(image = las_animated,
#             path = "las.gif")
image_write_gif(las_animated, path = "las.gif")

@@

```{r gif S, eval=T, out.width = "60%", out.height="60%"}
#, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"

path.image <- paste0(path, "/presentations/las.gif")
knitr::include_graphics(path.image)
```

@@

```{r Liverpool, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E08000012.png")
knitr::include_graphics(path.image)
```

@@

-   Spatial heterogeneity

-   Not a clear, easy to explain pattern

@@

-   Adoption heterogeneity

-   Different perceptions of risk and economic returns from new
    technologies

-   Early adopters vs. laggards, leapfrogging

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only05_av.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only95_av.png")
knitr::include_graphics(path.image)
```

## Rank dynamics and diffusion speed

-   Spatial heterogeneity

-   Expected volatility

# Spatial mechanisms

```{r, eval=FALSE, heatmaps, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

<!-- -   Website density regressions -- distance effect -->

-   Websites in Output Areas (c. 230,000)

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/la_ggplot/morani_la.csv")

```{r, eval=T, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/lisa/oa_ggplot/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

```{r lisa_la, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/la_ggplot/")

```{r lisa_oa, eval=T,results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/oa_ggplot/")

<!-- ## Website density regressions -->

<!-- <br> -->

<!-- $$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$ -->

<!-- <br> -->

<!-- ::: {style="margin-left: 50px !important; text-align:left !important"} -->

<!-- $Website\,Density_{i}$: -->

<!-- -   Websites per firm in a Local Authority $i$, *or* -->

<!-- -   Websites in an Output Area $i$ -->

<!-- ::: -->

<!-- ## Website density regressions -->

<!-- <br> -->

<!-- $$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$ -->

<!-- <br> -->

<!-- ::: {style="margin-left: 50px !important; text-align:left !important"} -->

<!-- $Place$: -->

<!-- -   London, *or* -->

<!-- -   Nearest city, *or* -->

<!-- -   Nearest retail centre -->

<!-- ::: -->

<!-- ## Website density regressions -->

<!-- <br> -->

<!-- $\beta$ interpretation: -->

<!-- -   The lower the $\beta$ is (or the larger the $|\beta|$ is)... -->

<!-- -   ... the larger urban gravitation is for web adoption. -->

<!-- ```{r b_London_la, fig.height=5, fig.width=5, message=FALSE} -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_london_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r b_city_la, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_city_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r b_centre_la,  fig.height=5, fig.width=5,message=FALSE} -->

<!-- #, out.height= "60%", out.width="60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_centre_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r b_London_oa, eval=T, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_london_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r b_centre_oa, eval = T,  fig.height=5, fig.width=5,message=FALSE} -->

<!-- #fig.height=4, fig.width=4,  -->

<!-- #, out.height= "60%", out.width="60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_city_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r b_city_oa, eval = T, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_centre_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ```{r r_squared, eval=T, results='asis'} -->

<!-- # This is for the RSquared of the different website density regressions. -->

<!-- path.in1 <- paste0(path, "/outputs/lisa/r2_all_oa.csv") -->

<!-- path.in2 <- paste0(path, "/outputs/lisa/r2_all_la.csv") -->

<!-- # read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>%  -->

<!-- #   ggplot(aes(x=year)) + -->

<!-- #   geom_line(aes(y=London, color = "OA to London"), size=1) + -->

<!-- #   geom_line(aes(y=cities, color = "OA to nearest city"), size=1) + -->

<!-- #   geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) + -->

<!-- #  -->

<!-- #   geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) + -->

<!-- #   geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) + -->

<!-- #   geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) + -->

<!-- #  -->

<!-- #   scale_color_discrete(name = "R-squared for regression:") + -->

<!-- #   #scale_linetype_manual(name = "Website density regressions111")  -->

<!-- #   ylab("R-squared") +  -->

<!-- #   ggtitle("Website density regressions") + -->

<!-- #   theme_minimal() + -->

<!-- #   theme(axis.title.x=element_blank(), -->

<!-- #         plot.title = element_text(hjust = 0.5)) -->

<!-- read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>%  -->

<!--   pivot_longer(!year, names_to = "regression", values_to = "Rsquared") %>%  -->

<!--   mutate(LA = if_else(str_ends(regression, ".LA"), " to LA", "to OA"), -->

<!--          regression = str_remove_all(regression, ".LA"), -->

<!--          line = paste0(regression, " ", LA)) %>%  -->

<!--   ggplot() + -->

<!--   geom_line(aes(x=year, y = Rsquared, color = line), -->

<!--             size = 1) + -->

<!--   scale_color_discrete(name = "R-squared for regression:") + -->

<!--   #scale_linetype_manual(name = "Website density regressions111")  -->

<!--   ylab("R-squared") +  -->

<!--   ggtitle("Website density regressions") + -->

<!--   theme_minimal() + -->

<!--   theme(axis.title.x=element_blank(), -->

<!--         plot.title = element_text(hjust = 0.5)) -->

<!-- #   scale_color_manual(values = c("red", "blue", "green")) -->

<!-- ``` -->

-   Spatial dependency
    -   Relatively small, consistent over time / scales
    -   London hot spot early on
    -   At local scale, consistent hotspots over time
    -   Granular analysis reveals other hotspots
        <!-- -   Distance effect -->
        <!--     -   Urban gravitation increases over time and then drops -->
        <!--     -   Granular analysis: gravitation -->
        <!--     -   Lost explanatory power over time -->

@@

> **Hierarchy effect**: from main centers to secondary ones -- central
> places

# Putting all of these together

## Modelling framework

-   [A hierarchy effect: from main centres to secondary
    ones]{style="color:orange;"}

-   [A neighborhood effect: first "hitting" nearby
    locations]{style="color:olive;"}

-   [S-shaped pattern in the cumulative level of
    adoption]{style="color:violet;"}

<br> <small>
$$Website\,Density_{t} \sim \color{orange}{Distance\,London} + 
\color{orange}{Website\,density\,London_{t-1}} + \\
\color{orange}{Distance\,Nearest\,City} + 
\color{orange}{Website\,density\,Nearest\,City_{t-1}} + \\
\color{orange}{Distance\,Nearest\,Retail_{i}} +
\color{orange}{Website\,density\,Nearest\,Retail_{t-1}} +\\
\color{olive}{W*\, Website\,density_{t-1}} +\\ 
\color{violet}{year_{t}}$$ </small>

## Modelling framework

-   Random forests to predict $Website\,Density_{i,t}$

-   2 spatial resolutions:

    -   Local Authorities (websites per firm)
    -   Output Areas (websites)

-   2 sets of models:

    -   All the data ⟹ *variable importance*
    -   Train on all but one region, test on the holdout region ⟹
        *spatial differences and similarities* of diffusion mechanisms

-   Space-time sensitive 10-fold CV (`CAST`)

## Models trained on all data

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.032 | 0.810    | 0.019 |
| Output Areas        | 5.000 | 0.205    | 1.047 |

<small> \*No retail centre predictors for the Local Authority models
</small>

## Variable importance for Local Authorities

```{r varimpLA, eval = T, out.height= "58%", out.width="58%", message=FALSE}

path.image <- paste0(path, "/outputs/rf/figures/varimp_LA.png")
knitr::include_graphics(path.image)
```

## Variable importance for Output Areas

```{r varimpOA, eval = T, out.height= "58%", out.width="58%", message=FALSE}
#,  fig.height=5, fig.width=5,message=FALSE

path.image <- paste0(path, "/outputs/rf/figures/varimp_OA.png")
knitr::include_graphics(path.image)
```

## Regional similarities

```{r similarity, eval = T, message=FALSE}
path.lad <- paste0(path, "/outputs/rf/figures/test_regions_LA.csv")
path.oa <- paste0(path, "/outputs/rf/figures/test_regions_OA.csv")

lad <- read.csv(path.lad) %>% 
  rename('RSquared LAD' = Rsquared)

oa <- read.csv(path.oa) %>% rename(Region = test.region,
                                   'RSquared OA' = Rsquared)

lad %>% left_join(oa) %>% 
  mutate('Rank OA' = rank(desc(`RSquared OA`)),
         'Rank LAD' = rank(desc(`RSquared LAD`))) %>% 
  relocate(5, .after = 2) %>% 
  arrange(`Rank LAD`) %>% 
  kable(digits=3)
```

## Alternative specification: growth, trained on all data

<br> <small>
$$Website\,Density\,Growth_{t} \sim \color{orange}{Distance\,London} + 
\color{orange}{Website\,density\,London_{t-1}} + \\
\color{orange}{Distance\,Nearest\,City} + 
\color{orange}{Website\,density\,Nearest\,City_{t-1}} + \\
\color{orange}{Distance\,Nearest\,Retail_{i}} +
\color{orange}{Website\,density\,Nearest\,Retail_{t-1}} +\\
\color{olive}{W*\, Website\,density_{t-1}} +\\ 
\color{violet}{year_{t}}$$ </small>

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.200 | 0.634    | 0.148 |

<small> \*No retail centre predictors for the Local Authority models
</small>

## Alternative specification: growth, trained on all data

```{r growth LA}
path.table <- paste0(path, "/outputs/rf/figures/test_regions_LA_growth.csv")
read.csv(path.table) %>% 
  mutate(Rsquared = round(Rsquared, digits= 3)) %>% 
  arrange(desc(Rsquared)) %>% 
  kable()
```

-   Established technological diffusion spatial processes still apply

    -   for a digital technology
    -   at local scales

-   Geography matters: spatial dependency, urban gravitation

-   Hierarchical diffusion

@@

-   Stability and volatility: leapfrogging, early adopters dropping, but
    also stable positions

-   Spatially consistent mechanisms at local scale

-   Regional heterogeneity

>>>>

---
title: 'Digital economy in the UK: an evolutionary story'
# date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
author: |
  |
  | Emmanouil Tranos
  |
  | <small>University of Bristol, Alan Turing Institute</small>
  | <small>e.tranos@bristol.ac.uk, [\@EmmanouilTranos](https://twitter.com/EmmanouilTranos), [etranos.info](https://etranos.info/)</small>
output: 
  revealjs::revealjs_presentation:
    theme: simple
    self_contained: true
    reveal_options:
      width: 1150
      height: 720
bibliography: bibliography.bib
biblio-style: "apalike"
css: style.css
editor_options: 
  markdown: 
    wrap: 72
---

@@

::: {style="margin-left: 50px !important; text-align:left !important"}
-   Introduction
-   Web data
-   Spatial analysis
-   S-shaped diffusion curves
-   Rank dynamics
-   Conclusions <br> <br>
    <!-- [etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/) -->
:::

@@

## Aims

-   Map the **active** engagement with the *digital*
-   Over time, **early stages** of the internet
-   **Granular** and **multi-scale** spatial perspective

## Aims

@@

-   Understand how the adoption of new technologies evolves

@@

@@

-   Archived web data

@@

-   Geolocate:

    - to a unique postcode

    - to multiple postcodes

-------------------------------------------

@@

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"}

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"}

@@

<small>

-   Tranos, E., and C. Stich. 2020. Individual internet usage and the
    availability of online content of local interest: A multilevel
    approach. *Computers, Environment and Urban Systems*, 79:101371.

-   Tranos, E., T. Kitsos, and R. Ortega-Argilés. 2021. Digital economy
    in the UK: Regional productivity effects of early adoption.
    *Regional Studies*, 55:12, 1924-1938.

-   Stich, C., E. Tranos and M. Nathan. 2022. Modelling clusters from
    the ground up: a web data approach. *Environment and Planning B*, in
    press.

-   Tranos, E., A. C. Incera and G. Willis. 2022. Using the web to
    predict regional trade flows: data extraction, modelling, and
    validation, *Annals of the AAG*, in press.

</small>

@@

20080509162138/<http://www.website1.co.uk/contact_us> IG8 8HD

@@

# load 2000 co.uk
# setwd("C:/Users/TranosE/DataShare/archive/nuts")
path.2000 <- "C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/all2000couk.csv"

@@

![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

# Web diffusion

## Mapping website density

```{r heatmaps, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

---

-   Website density regressions -- distance effect

-   Websites in Output Areas (c. 200,000)

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/morani_la.csv")

```{r, eval=T, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/lisa/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/lisa/")

```{r lisa_oa, eval=T,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/lisa/")

## Website density regressions

$$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$

::: {style="margin-left: 50px !important; text-align:left !important"}
$Website\,Density_{i}$:

-   Websites per firm in a Local Authority $i$, *or*

-   Websites in an Output Area $i$

:::

## Website density regressions

$$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$

::: {style="margin-left: 50px !important; text-align:left !important"}
$Place$:

-   London, *or*

-   Nearest city, *or*

-   Nearest retail centre

:::

## Website density regressions

$\beta$ interpretation:

-   The lower the $\beta$ is (or the larger the $|\beta|$ is)...

-   ... the larger urban gravitation is for web adoption.

```{r b_London_la, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/lisa/b_dist_london_la.png")
knitr::include_graphics(path.image)
```

```{r b_city_la, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_city_la.png")
knitr::include_graphics(path.image)
```

```{r b_centre_la,  fig.height=5, fig.width=5,message=FALSE}
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

```{r b_London_oa, eval=T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

```{r b_centre_oa, eval = T,  fig.height=5, fig.width=5,message=FALSE}
#fig.height=4, fig.width=4, 
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

```{r b_city_oa, eval = T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

```{r r_squared, eval=T, results='asis'}
# This is for the RSquared of the different website density regressions.

path.in1 <- paste0(path, "/outputs/lisa/r2_all_oa.csv")
path.in2 <- paste0(path, "/outputs/lisa/r2_all_la.csv")

# read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
#   ggplot(aes(x=year)) +
#   geom_line(aes(y=London, color = "OA to London"), size=1) +
#   geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
#   geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +
# 
#   geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) +
#   geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) +
#   geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) +
# 
#   scale_color_discrete(name = "R-squared for regression:") +
#   #scale_linetype_manual(name = "Website density regressions111") 
#   ylab("R-squared") + 
#   ggtitle("Website density regressions") +
#   theme_minimal() +
#   theme(axis.title.x=element_blank(),
#         plot.title = element_text(hjust = 0.5))

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  pivot_longer(!year, names_to = "regression", values_to = "Rsquared") %>% 
  mutate(LA = if_else(str_ends(regression, ".LA"), " to LA", "to OA"),
         regression = str_remove_all(regression, ".LA"),
         line = paste0(regression, " ", LA)) %>% 
  ggplot() +
  geom_line(aes(x=year, y = Rsquared, color = line),
            size = 1) +
  scale_color_discrete(name = "R-squared for regression:") +
  #scale_linetype_manual(name = "Website density regressions111") 
  ylab("R-squared") + 
  ggtitle("Website density regressions") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

#   scale_color_manual(values = c("red", "blue", "green"))

```

- Spatial dependency
	- Relatively small and constant over time / scales
	- London hot spot early on
	- At local scale, consistent hotspots over time
	- Granular analysis reveals other hotspots

- Distance effect
	- Urban gravitation increases over time and then drops
	- Granular analysis: gravitation
	- Lost explanatory power over time

> **Hierarchy effect**: from main centers to secondary ones -- central
places

@@

```{r UK S, eval=T}
#, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"

path.image <- paste0(path, "/outputs/s_uk.png")
knitr::include_graphics(path.image)
```

```{r LA_S_gif, eval=F, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

library(magick)
las <- list.files(path = path.images, pattern = "^lad_", full.names = T) #%>% 
las_list <- lapply(las, image_read)

@@

## animate at 2 frames per second
las_animated <- image_animate(las_joined, fps = 2)

## view animated image
las_animated

## save to disk
image_write(image = las_animated,
            path = "las.gif")

@@

@@

```{r Liverpool, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E08000012.png")
knitr::include_graphics(path.image)
```

@@

- Spatial heterogeneity
- Not clear pattern

@@

- Adoption heterogeneity 
- Perceptions of risk and economic returns from new technologies
- Early adopters vs. laggards, leapfrogging

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only05.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only95.png")
knitr::include_graphics(path.image)
```

----

@@

-   **Geography matters:** spatial dependency, urban gravitation

-   Some indications of a hierarchical diffusion

@@

-   Well-established theoretical approaches of diffusion survive even at
    a granular level

-   Stability and volatility: leapfrogging, early adopters dropping, but also maintaining

### 2025-01-21 src/la_RF_corrected.Rmd
early/late

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df,# %>% filter(year > 1999),                   # FILTER BY YEAR FOR GROWTH
                                spacevar = "ladcd",
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN21CD!=i), #& year > 1999),   # FILTER BY YEAR FOR GROWTH 
                                spacevar = "ladcd",
                                timevar = "year", 
                                k = 10)
  # CV
  tc <- trainControl(method = "cv", #MOVED HERE< DOUBLE CHECK
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   index = indices$index,
                   savePredictions = 'final')

@@

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df %>% filter(year > 1999),                     # FILTER BY YEAR FOR GROWTH
                                spacevar = "ladcd",
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN21CD!=i & year > 1999),      # FILTER BY YEAR FOR GROWTH 
                                spacevar = "ladcd",
                                timevar = "year", 
                                k = 10)
  # CV
  tc <- trainControl(method = "cv", #MOVED HERE< DOUBLE CHECK
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   index = indices$index,
                   savePredictions = 'final')

>>>>

library(tidyverse)
library(rprojroot)
# library(rgdal)
# library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df,# %>% filter(year > 1999),                   # FILTER BY YEAR FOR GROWTH
                                spacevar = "RGN21CD",                           # was ladcd in 1st submission
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN21CD!=i), #& year > 1999),   # FILTER BY YEAR FOR GROWTH 
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = 10)
  # CV
  tc <- trainControl(method = "cv", #MOVED HERE< DOUBLE CHECK
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   index = indices$index,
                   savePredictions = 'final')

@@

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df %>% filter(year > 1999),                     # FILTER BY YEAR FOR GROWTH
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN21CD!=i & year > 1999),      # FILTER BY YEAR FOR GROWTH 
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = 10)
  # CV
  tc <- trainControl(method = "cv", #MOVED HERE< DOUBLE CHECK
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   index = indices$index,
                   savePredictions = 'final')

### 2025-01-21 src/oa_RF_corrected.Rmd
early/late

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df, 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = k)

>>>>

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df, 
                                spacevar = "RGN11CD",
                                timevar = "year", 
                                k = 10)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = k)
